Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-09-20 paper.tex
Iteration definitions section 2

In this paper, a workflow is a set of tasks alongside a description of their
properties and relations. Each task may have an arbitrary number of properties
like number of cores, executables, or input/output files. Tasks may have
precedence relations depending on their data dependences or any other type of
dependency mandated by the application algorithms. Tasks with precedence
relations have to be executed serially, otherwise tasks can be executed
concurrently. A workload is defined as a set of tasks that can be executed
concurrently. As such, a workflow can be composed by a set of workloads.

The terms ``task'' and ``job'' are also used inconsistently across communities
that perform scientific computing. In this paper, a task is a \ldots
\mtnote{Are we going to use task and job as defined in Jedi and Panda Server?}

Usually, workflows are represented as graphs where tasks are vertices and
their relations edges~\cite{}. Often, graphs are supposed to be acyclic but
graphs with cycles have been used to represent workflows of workflows. In this
paper, a workflow template is a type of graph while a workflow instance is a
type of graph with a specific set of vertices and edges. Further, a graph is
``abstract'' when no resource properties are available for all vertices,
``concrete'' otherwise~\cite{}.

The distinction between an abstract and concrete graph highlights an important
element of the execution process of a workflow. Workflows can be specified
without indicating on what resources they should be executed. Accordingly, an
abstract workflow can be interpreted as a formal description of the
requirements for the workflow execution. Once these requirements are matched
by a set of resource capabilities, an abstract workflow becomes a concrete
workflow, i.e. a formal description of the workflow execution process and its
execution environment.

>>>>

In this paper, we use the following definitions:

\begin{description}
  \item[Task]     A set of operations to be performed on a computing platform,
                  alongside a description of the properties and dependences of
                  those operations, and indications on how they should be
                  executed and satisfied.
  \item[Workload] A set of tasks that can be executed concurrently, possibly
                  related by a set of relations. For example, tasks of a workload can share one or more input files or communicate during execution.
  \item[Workflow] Set of workloads, related by a set of relations that define
                  the order in which each workload can be executed. Data
                  dependences are the most common relations among workloads,
                  used to define the precedence among their executions. Note
                  that, formally, a workload can have a single task.
\end{description}

Each task may have an arbitrary number of properties like number of cores,
executables, or input/output files. Tasks may have precedence relations
depending on their data dependences or any other type of dependency mandated
by the application algorithms. Tasks with precedence relations have to be
executed serially, otherwise tasks can be executed concurrently. A workload is
defined as a set of tasks that can be executed concurrently. As such, a
workflow can be composed by a set of workloads.

The terms ``task'' and ``job'' are also used inconsistently across communities
that perform scientific computing. In this paper, ``job'' refers to the entity
that is submitted to a local resource management system (LRMS), like a batch
system or a scheduler. As such, a task can become a job when is scheduled on a
resource that exposes a LRMS but can also become a virtual machine or a
container when bootstrapped on an infrastructure supporting virtualization.

Usually, workflows are represented as graphs where tasks are vertices and
their relations are edges~\cite{}. Often, graphs are supposed to be acyclic
but graphs with cycles have been used to represent workflows of
workflows~\cite{}. In this paper, a workflow template is a type of graph while
a workflow instance is a type of graph with a specific set of vertices and
edges. Further, a graph is ``abstract'' when no resource properties are
available for all vertices, ``concrete'' otherwise~\cite{}.

The distinction between an abstract and concrete graph highlights an important
element of the execution process of a workflow. Workflows can be specified
without indicating on what resources they should be executed. Accordingly, an
abstract graph can be interpreted as a formal description of the requirements
for the workflow execution. Once these requirements are matched by a set of
resource capabilities, the graph becomes concrete, i.e. a formal description
of the workflow execution process and its execution environment.
